---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```


# rjdworskpace

[![Travis Build Status](https://img.shields.io/travis/AQLT/rjdworkspace.svg?logo=travis)](https://travis-ci.org/AQLT/rjdworkspace)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rjdworkspace)](https://cran.r-project.org/package=rjdworkspace)

## Overview

rjdworkspace gives a set of tools to manipulate `JDemetra+` workspaces.
It depends on the .jar files of [RJDemetra](https://github.com/nbbrd/rjdemetra) and extend some functions.
In particular, rjdworkspace allows  to:

- update the metadata of a workspace from those contained in another one (`update_metadata()`, `update_metadata_roughly()`) or update the metadata of a SaItem with the metadata contained in another SaItem (`set_metadata()`) ;  
- replace, remove or add a SaItem in a workspace (`remove_sa_item()`, `remove_all_sa_item()`, `replace_sa_item()`, `add_new_sa_item()`);  
- get and set the comment of a SaItem (`get_comment()`, `set_comment()`);
- set the specification of a model contains in a SaItem (`set_spec()`).

## Installation

rjdworkspace relies on RJDemetra that requires Java SE 8 or later version.

```{r gh-installation, eval = FALSE}
# Install development version from GitHub
# install.packages("devtools")
devtools::install_github("AQLT/rjdworkspace")
```
